---
title: "Covid_19"
output: html_notebook
---

# Install package and clean global env
```{r}
require("COVID19")
rm(list = ls())
```




# Some functions to use
```{r}
source("tools.R")
```

# Retrieve data
## European countries

```{r} 
countries <- c("BEL","CHE","DNK","ALB", "BGR","CYP","EST", "AND","BIH", "CZE","FIN","AUT","BLR", "DEU",
               "DNK","HRV","ISL","FRA","GBR","HUN","ITA","GRC", "IRL", "LIE")
europe    <- sapply(countries, function(x) {print(x);return(get_data(x, obj.name = "data.europe"))})
summary.europe <- summary(data.europe)
```

## North America
```{r} 
countries             <- c("ATG","BHS", "BRB", "BMU","CAN", "CRI", "USA", "CUB","DMA","DOM","SLV","GRD", "GTM", 
                           "HTI", "HND", "JAM", 'MEX', "NIC", "PAN","PRI","TTO","VIR")
north.america         <- sapply(countries, function(x) {print(x);return(get_data(x, obj.name = "data.north.america"))})
summary.north.america <- summary(data.north.america)
```


## South America
```{r} 
countries             <- c("ARG", "BOL", "BRA", "CHL", "COL", "ECU", "GUY", "PRY", "PER", "SUR", "URY","VEN")
south.america         <- sapply(countries, function(x) {print(x);return(get_data(x, obj.name = "data.south.america"))})
summary.south.america <- summary(data.south.america)
```   


## Oceania
```{r} 
countries       <- c("AUS","NZL")
oceania         <- sapply(countries, function(x) {print(x);return(get_data(x, obj.name = "data.oceania"))})
summary.oceania <- summary(data.oceania)
```   




## Asia
```{r} 
countries       <- c("AFG","ARM","AZE","BHR","BGD","BTN","BRN","KHM","CHN","GEO","IND","IDN","IRN","IRQ","ISR","JPN","JOR",
                     "KAZ","KWT","KGZ","LAO","LBN","MYS","MDV","MNG", "NPL","OMN","PAK","PSE","PHL","QAT","SAU", "SGP","KOR","LKA","SYR","TWN","TJK","THA","TUR",
                     "ARE","UZB","VNM","YEM")
asia         <- sapply(countries, function(x) {print(x);return(get_data(x, obj.name = "data.asia"))})
summary.asia <- summary(data.asia)
```   

  



## Africa
```{r} 
countries      <- c("AGO", "BEN", "BWA", "BFA", "BDI","CMR","CPV", "CAF", "TCD", "COM","COG","COD","DJI","EGY","GNQ","ERI","SWZ","ETH","GAB","GMB","GHA",
                    "GIN","GNB","CIV","KEN","LSO","LBR","LBY","MDG","MWI","MLI","MRT","MUS","MAR","MOZ","NAM","NER","NGA","STP","RWA","STP", "RWA","STP",
                    "SEN","SYC","SLE","SOM","ZAF","SSD", "SDN","SWZ","TZA","TGO","TUN","UGA","COD","ZMB","TZA","ZWE")
africa         <- sapply(countries, function(x) {print(x);return(get_data(x, obj.name = "data.africa"))})
summary.africa <- summary(data.africa)
```   

## Merge all the data
```{r}
data.all.continents <- rbind(data.north.america, data.oceania, data.europe, data.south.america, data.africa)
summary.all.continents <- summary(data.all.continents)
```

## Data properties
### Europe
```{r}
dim(data.europe)
```   
### North.America
```{r}
dim(data.north.america)
```
### South.America
```{r}
dim(data.south.america)
```
### Oceania
```{r}
dim(data.oceania)
```
### Asia
```{r}
dim(data.asia)
```
### Africa
```{r}
dim(data.africa)
```   
### All continents
```{r}
dim(data.all.continents)
```


# Analysis
## summaries
### Europe
```{r}
summary.europe
```   
### North.America
```{r}
summary.europe
```
### South.America
```{r}
summary.south.america
```
### Oceania
```{r}
summary.oceania
```
### Asia
```{r}
summary.asia
```
### Africa
```{r}
summary.africa
```   
### All continents
```{r}
summary.all.continents
```

## Ranks 
### Europe
```{r}
ranks.europe <- as.data.frame(sapply(data.europe, rank))
summary(ranks.europe)
```

### North America
```{r}
ranks.north.america <- as.data.frame(sapply(data.north.america, rank))
summary(ranks.north.america)
```

### South America
```{r}
ranks.south.america <- as.data.frame(sapply(data.south.america, rank))
summary(ranks.south.america)
```
### Oceania
```{r}
ranks.oceania <- as.data.frame(sapply(data.oceania, rank))
summary(ranks.oceania)
```

### Asia
```{r}
ranks.asia <- as.data.frame(sapply(data.asia, rank))
summary(ranks.asia)
```

### Africa
```{r}
ranks.africa <- as.data.frame(sapply(data.africa, rank))
summary(ranks.africa)
```
# Wilcox.test
## Europe 
```{r}
wilcox.test(data.europe$confirmed,data.africa$confirmed)

```

```{r}
wilcox.test(data.europe$confirmed,data.asia$confirmed)
```       
```{r}
wilcox.test(data.europe$confirmed,data.south.america$confirmed)
```
```{r}
wilcox.test(data.europe$confirmed,data.north.america$confirmed)
```
```{r}
wilcox.test(data.europe$confirmed,data.oceania$confirmed)
```
